---
title: "writing_functions"
output: html_document
date: "2023-10-26"
---

Load key packages and graphing settings: 

```{r setup, message = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

```

Set seed for reproducibility 
```{r}
set.seed(12345)
```

### Z score function

Z scores subtract the mean and divide the sd. 
```{r}
x_vec = rnorm(20, mean = 5, sd = .3)
```
 
Compute Z score for 'x_vec'
```{r}
(x_vec - mean (x_vec)) / sd(x_vec)
```

Write a function to do this! 
```{r}
z_score = function (x) {
  
  if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if(length(x) < 2) {
    stop("You need at least 2 arguments to get z score")
  }
  
  z = (x- mean(x)) / sd(x)
  
  z
  
}
```

Check that it works. 
```{r}
z_score(x = x_vec)
```

Keep checking 
```{r, error = TRUE}
z_score(x = 3)

z_score(c("my", "name", "is", "grace"))

z_score(c(TRUE, TRUE, FALSE, TRUE))

z_score(iris)
```

### Multiple outputs. 

Write a function that returns the mean and sd from a sample of numbers. 
```{r}
mean_and_sd = function (x) {
  
  if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if(length(x) < 2) {
    stop("You need at least 2 arguments to get z score")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Double-checking this is correct... 
```{r}
mean_and_sd(x_vec)
```


### Start getting means and sds
```{r}
x_vec = rnorm(n = 30, mean = 5, sd = .5)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Now lets write a fucntion the uses "n", a true mean, and true sd as inputs
```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)

  tibble(
    mean = mean(x_vec),
    sd = sd(x_vec)
)
}

sim_mean_sd(n_obs = 3000, mu = 50, sigma = .5)

sim_mean_sd(12, 22, 4) #positional matching

```

### LOTR function: 
```{r}
lotr_func = function(path = "data/LotR_words.xlsx", cells, title){
  
  movie_df = readxl::read_excel(path, range = cells) |> 
    mutate(movie = title) |> 
    janitor::clean_names() |> 
    pivot_longer(
      female:male, 
      names_to = "sex",
      values_to = "words"
    ) |> 
    select(movie, everything())
    
  
  movie_df
}

lotr_df = 
  bind_rows(
    lotr_func(cells = "B3:D6", title = "fellowship_ring"),
    lotr_func(cells = "F3:H6", title = "two_towers"),
    lotr_func(cells = "J3:L6", title = "return_king"))
```

### NSDUH dataset: 
```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

data_marj = 
  nsduh_html |> 
  html_table() |> 
  nth(1) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
```

Now translating the above code into a function: 
```{r}
nsdhu_import = function(html, table_num, outcome) {
  
  html |> 
  html_table() |> 
  nth(table_num) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent),
    outcome = outcome) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
}

nsdhu_import(html = nsduh_html, table_num = 1, outcome = "marj")
nsdhu_import(html = nsduh_html, table_num = 4, outcome = "cocaine")
```

