---
title: "writing_functions"
output: html_document
date: "2023-10-26"
---

Load key packages: 

```{r setup, message = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

```

Set seed for reproducibility 
```{r}
set.seed(12345)
```

### Z score function

Z scores subtract the mean and divide the sd. 
```{r}
x_vec = rnorm(20, mean = 5, sd = .3)
```
 
Compute Z score for 'x_vec'
```{r}
(x_vec - mean (x_vec)) / sd(x_vec)
```

Write a function to do this! 
```{r}
z_score = function (x) {
  
  if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if(length(x) < 2) {
    stop("You need at least 2 arguments to get z score")
  }
  
  z = (x- mean(x)) / sd(x)
  
  z
  
}
```

Check that it works. 
```{r}
z_score(x = x_vec)
```

Keep checking 
```{r, error = TRUE}
z_score(x = 3)

z_score(c("my", "name", "is", "grace"))

z_score(c(TRUE, TRUE, FALSE, TRUE))

z_score(iris)
```

### Multiple outputs. 

Write a function that returns the mean and sd from a sample of numbers. 
```{r}
mean_and_sd = function (x) {
  
  if(!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if(length(x) < 2) {
    stop("You need at least 2 arguments to get z score")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Double-checking this is correct... 
```{r}
mean_and_sd(x_vec)
```


### Start getting means and sds
```{r}
x_vec = rnorm(n = 30, mean = 5, sd = .5)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Now lets write a fucntion the uases "n", a true mean, and true sd as inputs
```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)

  tibble(
    mean = mean(x_vec),
    sd = sd(x_vec)
)
}

sim_mean_sd(n_obs = 3000, mu = 50, sigma = .5)

sim_mean_sd(12, 22, 4) #positional matching

```

